\vspace{-.2in} Squint: Lossy Hierarchical Compression on Symbol Streams \vspace{-.1in}

### 2012-12-12 tex/paper.tex

\sectionfont{\large}
\subsectionfont{\normalsize}

@@

Overview

@@

Grammar Data Structure
Cluster Data Structure
Invariants Maintained
Core utility methods??
Linked Lists vs Arrays, Caching Expansions, Strings vs Symbols for expansion, Native Levenshtein

>>>>

\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalfont\itshape}

@@

Our full grammar compression scheme involves the following sequence of
operations and components:
\begin{enumerate}
  \item \Sequitur, which infers a CFG from the input stream.
  \item Lossifier algorithms, which take the \Sequitur grammar and simplify it,
    introducing lossiness.
  \item Reduction engine, which applies Kieffer and Yang's reduction rules to
    the lossified grammar.
\end{enumerate}

We implement all these components in the Ruby programming language.  Our
implementation of \Sequitur exactly mirrors the data structures and algorithm
described by Nevill-Manning and Witten \cite{sequitur}---and, empirically, it
has the same asymptotic running time---so we do not discuss it further.
However, we will examine in this section some of the techniques we used in
implementing \Similarity, \Cluster, and the reduction engine.

\subsubsection{CFG Representation}

Our representation of a context-free grammar is very similar to that used by
\Sequitur.  All of our rules are represented by a linked list of symbols;
however, unlike in \Sequitur, we omit refcounting and do not point from each
instance of a nonterminal symbol to its corresponding rule.  Instead, our rules
are kept in a hash table, mapping nonterminal symbols to a list representing
its RHS.

We chose to implement a list library rather than use Ruby's native arrays in
order to achieve better runtime for the splice operations.  Both \Sequitur and
our implementation of Kieffer and Yang's reductions require us to splice out a
subsequence of terminals from a rule, or to insert a subsequence (e.g., as a
result of inlining a singleton rule) into a rule.

Grammar Data Structure
Linked Lists vs Arrays, Caching Expansions, Native Levenshtein

\subsubsection{Lossifier Optimizations}

Perhaps the most crucial optimization we implement deals with the recursive
expansion of nonterminals into terminal strings.

@@
